checkData

### 2023-08-29 analysis/checkData.Rmd
Update checkData.Rmd

#Add COPE status FROM PRACTICE CODING, does not alter main d_journals tibble
```{r}
# Load googlesheet data

dj_prominent <- read_csv(here('data','raw', 'journals-prominent.csv')) %>% #loads csv of googlesheet data of prominent journals
  slice_head(n = 114) %>%
  select('journal' = 'journal_name', 'COPE' = 'COPE (T = member; F = not a member)' )

dj_random <- read_csv(here('data','raw', 'journals-random.csv')) %>% #loads csv of googlesheet data of random journals
  slice_head(n = 108) %>%
  select('journal' = 'journal_name', 'COPE' = 'COPE (T = member; F = not a member)' )

# Combine above CSVs to one tibble

dj_cope <- bind_rows(dj_prominent, dj_random)

# Identify duplicate rows
duplicates <- duplicated(dj_cope)

# Select the duplicate rows
duplicate_rows <- dj_cope[duplicates, ]

# Check if duplicate rows have the same COPE values for journals
for (i in seq_len(nrow(duplicate_rows))) {
  row <- duplicate_rows[i, ]
  id <- row$ID
  value <- row$Value
  same_values <- all(duplicate_rows$Value[duplicate_rows$ID == id] == value)

  if (same_values) {
    cat("Row", i, "with ID =", id, "has the same values in both columns.\n")
  } else {
    cat("Row", i, "with ID =", id, "has different values in both columns.\n")
  }
}

#All 14 duplicated (both sample) journals had consistent COPE status, remove duplicates
dj_cope <- distinct(dj_cope, journal, .keep_all = T)

#join with main data tibble:
d_primaryONLY <- left_join(d_primaryONLY, dj_cope, by = 'journal')

@@

@@

Firstly, specify PPC names that we want to convert to different haromized names.

```{r}
commentaries <- c("Brief comment", "Brief Comment")
letters <- c(

)
web_comments <- c()
```

```{r}
d_journals_final_eligible %>%
  mutate(name_harmonized = )
```

In Emotion, one line seems to be about ten words. So 260 lines is 2600 words.

>>>>

@@

## Harmonize reference limits

For reference limits we need to harmonize differences in data entry formatting. Additionally, when references are included in the overall length limit, we will re-code these as "NOT STATED", because no specific reference limit has been stated.

```{r}
d_journals_final_eligible <- d_journals_final_eligible %>% 
  mutate(ref_harmonized = str_remove_all(ref, pattern = '"'), #  remove any quotation marks
         ref_harmonized = str_remove(ref_harmonized, pattern = fixed("YES (provide number of references below), ")),# remove data entry question text
         ref_harmonized = str_remove(ref_harmonized, pattern = fixed("YES (copy and paste the limits in the 'other' section below), ")),# remove data entry question text
         ref_harmonized = case_when(
           ref_harmonized == "20 not hard-and-fast limits" ~ "20",
           ref_harmonized == "265 lines of text including references" ~ "NOT STATED",
           ref_harmonized == "contributions may have up to 15 references" ~ "15",
           ref_harmonized == "Included in 16 page overall limit" ~ "NOT STATED",
           ref_harmonized == "No more than 5 references" ~ "5",
           ref_harmonized == "overall limit is 265 lines of text including references" ~ "NOT STATED",
           TRUE ~ ref_harmonized
         )) 
```

@@

Firstly, specify PPC names that we want to convert to different harmonized names.

```{r}
commentaries <- c("Brief comment", "Brief Comment", "commentaries", "Commentaries", "Commentary", "Comments", "Matters Arising", "Observations & Commentaries", "Open peer commentaries", "Short Communications and Commentaries", "Short Research Notes", "Text review")
letters <- c("Letter", "Letters", "Letter to the editor", "Letters to the editor", "letters to the editor", "Letters to the Editor.", "letters to the editors", "Letters to the Editors")
# web_comments <- c()
other <- c("Verification reports")
```

```{r}
d_journals_final_eligible <- d_journals_final_eligible %>%
  mutate(name_harmonized = case_when(
    name %in% commentaries ~ "Commentary",
    name %in% letters ~ "Letters",
    name %in% other ~ "Other"
  ))
```
